---
title: "Reliability"
output: html_document
date: "`r Sys.Date()`"
author: "Sarah Wu"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(dplyr)
library(lavaan)
library(MBESS)
library(rstatix)
library(papaja)
```

## Data Preparation

```{r}
iriss <- read_csv("data/iriss_trial_data.csv") %>% 
  mutate(condition = str_to_title(condition))

convos <- read_csv("data/evaluated_compliant_conversations.csv")
```

```{r}
# Only include submitter_id in iriss that appear in convos
iriss_included <- iriss %>% 
  semi_join(convos, 
            by = c("submitter_id", "condition")) 

intrinsic_motivation_items <- iriss_included %>% 
  select(submitter_id,
         starts_with("intrinsic_motivation")) %>% 
  mutate(across(.cols = starts_with("intrinsic_motivation"), as.numeric)) %>% 
  distinct() %>% 
  select(-submitter_id)

consideration_aid_items <- iriss_included %>% 
  select(submitter_id,
         starts_with("consideration_aid")) %>% 
  mutate(across(.cols = starts_with("consideration_aid"),
                as.numeric)) %>% 
  distinct() %>% 
  select(-submitter_id) %>% 
  drop_na()


```

## Purpose of Measures Section

The purpose of the Measures section is to describe the scales used in the study and to report the reliability of these scales. In this analysis, we will use McDonald's omega to evaluate the internal consistency of the intrinsic motivation scale and the consideration aid scale. It is relevant for internal validity because it provides evidence that the items within each scale are measuring the same underlying construct. It is relevant for external validity because it supports the generalizability of the findings by demonstrating that the scales are reliable measures that can be used in future research on human-AI collaboration for creative ideation, not just for the Alternative Uses Task used in this study.

## Measures

We used two scales from prior research on human-AI collaboration for creative ideation. The 4-item Task-Level Intrinsic Motivation scale (Shin & Grant, 2019) was designed to assess participants' intrinsic motivation to complete the creative ideation task. While this scale was originally designed to assess intrinsic motivation for sales employees' core tasks (e.g., selling, product learning), the individual items were broad enough that we adapted it for use in assessing intrinsic motivation in the Alternative Uses Task, in which participants are asked to generate creative uses for everyday objects. Specifically, participants were asked to rate the extent to which they found the task "interesting," "enjoyable," "fun," and "engaging." Participants rated these items on a 7-point Likert scale (1 = not at all, 7 = completely).

The 3-item Consideration Aid scale (Lee & Chung, 2024) was adapted from a study on human-AI collaboration in a product generation task to assess the extent to which participants felt that AI helped them consider other aspects of the object for which they were asked to generate alternative uses. The items were "AI helped me think of important aspects of the object that I would not have considered otherwise," "AI made me consider some unique angle of viewpoints that I would not have considered otherwise," and "AI made me realize various aspects of the object that were important in my idea generation." Participants rated these items on a 7-point Likert scale (1 = strongly disagree, 7 = strongly agree).

McDonald's omega (McDonald, 1999) was calculated for both scales to assess their internal consistency. The results of the reliability analysis are reported below.

```{r}

options(warn = -1)

MBESS::ci.reliability(intrinsic_motivation_items, 
                      type = "omega",
                      interval.type = "perc",
                      conf.level = 0.95)

MBESS::ci.reliability(consideration_aid_items, 
                      type = "omega",
                      interval.type = "perc",
                      conf.level = 0.95)
```

The results of the reliability analysis indicate that the intrinsic motivation scale has a McDonald's omega of 0.92 [95% CI: 0.90-0.95], which suggests excellent internal consistency. The consideration aid scale has a McDonald's omega of 0.86 [95% CI: 0.78-0.92], which also indicates good internal consistency. These results suggest that both scales are reliable measures for assessing intrinsic motivation and consideration aid in the context of human-AI collaboration for creative ideation.

Responses to the individual items of each scale were averaged to create composite scores for intrinsic motivation and consideration aid, which were used in subsequent analyses to examine the effects of AI assistance on participants' motivation and their perceptions of the AI's contribution to their idea generation process. Higher scores on the intrinsic motivation scale indicate greater intrinsic motivation to complete the creative ideation task, while higher scores on the consideration aid scale indicate a stronger perception that the AI provided helpful assistance in considering different aspects of the object for idea generation.

```{r}

# Compute rowwise means and SDs for intrinsic motivation and consideration aid
intrinsic_motivation_items %>% 
  rowwise() %>% 
  mutate(intrinsic_motivation = mean(c_across(starts_with("intrinsic_motivation")), 
                                     na.rm = TRUE)) %>% 
  ungroup() %>% 
  select(intrinsic_motivation) %>%
  rstatix::get_summary_stats(intrinsic_motivation, type = "mean_sd")


consideration_aid_items %>% 
  rowwise() %>%
  mutate(consideration_aid = mean(c_across(starts_with("consideration_aid")),
                                  na.rm = TRUE)) %>%
  ungroup() %>%
  select(consideration_aid) %>%
  rstatix::get_summary_stats(consideration_aid, type = "mean_sd")
```

Overall, intrinsic motivation was relatively high among participants (M = 5.08, SD = 1.35), suggesting that participants generally found the creative ideation task to be interesting and enjoyable. The consideration aid scale a moderate mean score (M = 4.67, SD = 1.43), indicating that participants generally felt that the AI provided helpful assistance in considering different aspects of the object for idea generation. These descriptive statistics provide context for interpreting the effects of AI assistance on participants' motivation and perceptions of the AI's contribution in subsequent analyses.